Exp130: Sparse coordination - general experiment analysis.

### 2019-07-18 voltagebudget/analysis/exp132_analysis.Rmd
exp132 analysis

# Sparse exps
exp <- "131a_780"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_781"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_782"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_783"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_784"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_785"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "131a_786"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# Org dense code
exp <- "131b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
tmp$N_oscs <- rep(250, nrow(tmp))

@@

```{r}
avg_results %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=as.factor(N_oscs))) +
  # geom_line(size=1, alpha=0.6) +
  geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

>>>>

# Sparse exps
exp <- "132a_780"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_781"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_782"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_783"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_784"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_785"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "132a_786"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# Org dense code
exp <- "132b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
tmp$N_oscs <- rep(250, nrow(tmp))

@@

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 1) %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=as.factor(N_oscs))) +
  # geom_line(size=1, alpha=0.6) +
  geom_point(size=2, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```
